manuscript_outline

### 2025-06-17 docs/manuscript/paper.Rmd
table styling
change render output so figure links work

---
title: ""
output: pdf_document
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: apa.csl
bibliography: references.bib
---

>>>>

---
title: ""
output:  
  bookdown::pdf_document2:
    toc: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: apa.csl
bibliography: references.bib
---
